Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-02-01 paper/elsarticle/main.tex
Paper: Theory: update

	%% TODO: DEF RULE/CONDITION GAMMA

	\begin{definition}
		\label{def:rho_tilde}
		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the decision parameter $\gamma$, $0 \leq \gamma \leq 1$. Then the scaling tuning parameter $\widetilde{\rho}$ is given by:		
		\begin{eqnarray}
			\label{eq:rho_tilde_def}
			\widetilde{\rho} = \left\{ 
			\begin{matrix}
				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} ), \\
				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle,
			\end{matrix}
			\right.
		\end{eqnarray}
		where $0 \leq \rho_{\mathrm{s}} \leq 1$ holds.
		\end{definition}

@@

	\begin{remark}
		\label{rem:rho_tilde}
		Note, the introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals. If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each interval. Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in the analogous way.
	\end{remark}

	The following outcomes result from Eq.~\eqref{eq:rho_up}.

	\begin{lemma}
		\label{lem:PWA_control_law_interval}
		% TODO: Convert to Lemma
		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaling tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}. Then the control law  approximated into the form:
		\begin{eqnarray}
			\label{eq:PWA_control_law_interval}
			u(k) = (1-\widetilde{\rho}(k)) \, u_\mathrm{L}(k) + \widetilde{\rho}(k) \, u_\mathrm{U}(k),
		\end{eqnarray}
		preserves the closed-loop system stability and recursive feasibility of the original control law in~\eqref{eq:PWA_control_law}.
		% 
		% The following outcomes result from Eq.~\eqref{eq:rho_up}. If $\rho=0$, then $\widetilde{\rho} = 0$. When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$. In such a way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value. Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
	\end{lemma}

	\begin{proof}
		\label{proof:rho_tilde}
		. 
	\end{proof}

	\begin{corollary}
		The following outcomes result from Eq.~\eqref{eq:rho_down}. When $\rho=0$, $\widetilde{\rho} = \rho_{\mathrm{s}}$. When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$. In such a way, the parameter $\rho$ can be scaled in the second part of the interval from the splitting value up to 1. Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
	\end{corollary}

>>>>

	%% TODO: DEF RULE/CONDITION GAMMA
	\begin{definition}[Decision function]
		\label{def:gamma}
		For given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho < 1$ be a boundary value splitting an interval into the two parts. Let $\gamma: \mathbb{R} \rightarrow \mathbb{R}$ be an arbitrary function such that $0 \leq \gamma \leq 1$ holds. Then the decision function $\gamma$ is constructed to assign its value either $\gamma \leq \rho_{\mathrm{s}}$ or $\gamma > \rho_{\mathrm{s}}$.
	\end{definition}

	\begin{definition}[Scaling tuning parameter]
		\label{def:rho_tilde}
		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the value of the decision function $\gamma$, $0 \leq \gamma \leq 1$. Then the scaling tuning parameter $\widetilde{\rho}$ is given by:		
		\begin{eqnarray}
			\label{eq:rho_tilde_def}
			\widetilde{\rho} = \left\{ 
			\begin{matrix}
				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} \rangle , \\
				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle,
			\end{matrix}
			\right.
		\end{eqnarray}
		where $0 \leq \rho_{\mathrm{s}} \leq 1$ holds.
		\end{definition}

@@

	\begin{remark}
		\label{rem:rho_tilde}
		The introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals. If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each part of the interval. Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in the analogous way.
	\end{remark}

	The following outcomes result from Eq.~\eqref{eq:rho_tilde_def}. 
	%	\begin{corollary}
	% The following outcomes result from Eq.~\eqref{eq:rho_up}. If $\rho=0$, then $\widetilde{\rho} = 0$. When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$. In such a way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value. Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.		
	%	\end{corollary}
	%
	%	\begin{corollary}
	%		The following outcomes result from Eq.~\eqref{eq:rho_down}. When $\rho=0$, $\widetilde{\rho} = \rho_{\mathrm{s}}$. When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$. In such a way, the parameter $\rho$ can be scaled in the second part of the interval from the splitting value up to 1. Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
	%	\end{corollary}
	\begin{lemma}
		\label{lem:PWA_control_law_interval}
		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaling tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}. Then the control law  approximated into the form:
		\begin{eqnarray}
			\label{eq:PWA_control_law_interval}
			u(k) = (1-\widetilde{\rho}(k)) \, u_\mathrm{L}(k) + \widetilde{\rho}(k) \, u_\mathrm{U}(k),
		\end{eqnarray}
		preserves the closed-loop system stability and recursive feasibility of the original control law in~\eqref{eq:PWA_control_law}.
	\end{lemma}

	\begin{proof}
		\label{proof:rho_tilde}
		It has been proven~\cite{Oravec_tunable} that for the asymptotic stable and recursive feasible pair of control inputs $(u_{\mathrm{L}}, u_{\mathrm{U}})$, the approximated control law in~\eqref{eq:PWA_control_law} preserves these properties for any $\rho$ satisfying $0 \leq \rho \leq 1$, see Theorem~3.6 in~\cite{Oravec_tunable}. 
		% 
		It remains to prove that for any value of the scaling tuning parameter $\widetilde{\rho}$ according to the Definition~\ref{def:rho_tilde} the same results hold. 
		The rest of the proof of Lemma~\ref{lem:PWA_control_law_interval} consists of two parts. 
		\\
		First, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
		$\widetilde{\rho} = 0$. 
		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = \rho_{\mathrm{s}} < 1$. Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $0 < \widetilde{\rho} < \rho_{\mathrm{s}} $ holds. 
		Therefore, any value of $\widetilde{\rho}$ satisfy $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$. As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved. 
		\\
		Secondly, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
		$\widetilde{\rho} = \rho_{\mathrm{s}}$. 
		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = 1$. Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $\rho_{\mathrm{s}} < \widetilde{\rho} < 1 $ holds. 
		Therefore, any value of $\widetilde{\rho}$ satisfy $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$. As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved. 
		% The rest of the proof follows the proof of the Theorem~3.6 in~\cite{Oravec_tunable}. 
	\end{proof}

	\begin{remark}
		The Lemma~\ref{lem:PWA_control_law_interval} can be extended subject to the multiple intervals in an analogous way following the Remark~\ref{rem:rho_tilde}.
	\end{remark}
